---
title: "Week5"
author: "JonPuritz"
date: "2/27/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Creating a reference with data

## 1.  Load conda environment for dDocent

```{bash eval=FALSE}
conda create -n Week5 ddocent
conda activate Week5
```

```{bash}
source activate Week5
ReferenceOpt.sh
```

```{bash eval=FALSE}
source activate Week5
ReferenceOpt.sh 2 4 2 4 PE 64 0.9 0.98 0.01
```
```
K1 is 2 K2 is 2 c is 0.90
K1 is 2 K2 is 2 c is 0.91
K1 is 2 K2 is 2 c is 0.92
K1 is 2 K2 is 2 c is 0.93
K1 is 2 K2 is 2 c is 0.94
K1 is 2 K2 is 2 c is 0.95
K1 is 2 K2 is 2 c is 0.96
K1 is 2 K2 is 2 c is 0.97
K1 is 2 K2 is 2 c is 0.98
K1 is 2 K2 is 3 c is 0.90
K1 is 2 K2 is 3 c is 0.91
K1 is 2 K2 is 3 c is 0.92
K1 is 2 K2 is 3 c is 0.93
K1 is 2 K2 is 3 c is 0.94
K1 is 2 K2 is 3 c is 0.95
K1 is 2 K2 is 3 c is 0.96
K1 is 2 K2 is 3 c is 0.97
K1 is 2 K2 is 3 c is 0.98
K1 is 2 K2 is 4 c is 0.90
K1 is 2 K2 is 4 c is 0.91
K1 is 2 K2 is 4 c is 0.92
K1 is 2 K2 is 4 c is 0.93
K1 is 2 K2 is 4 c is 0.94
K1 is 2 K2 is 4 c is 0.95
K1 is 2 K2 is 4 c is 0.96
K1 is 2 K2 is 4 c is 0.97
K1 is 2 K2 is 4 c is 0.98
K1 is 3 K2 is 2 c is 0.90
K1 is 3 K2 is 2 c is 0.91
K1 is 3 K2 is 2 c is 0.92
K1 is 3 K2 is 2 c is 0.93
K1 is 3 K2 is 2 c is 0.94
K1 is 3 K2 is 2 c is 0.95
K1 is 3 K2 is 2 c is 0.96
K1 is 3 K2 is 2 c is 0.97
K1 is 3 K2 is 2 c is 0.98
K1 is 3 K2 is 3 c is 0.90
K1 is 3 K2 is 3 c is 0.91
K1 is 3 K2 is 3 c is 0.92
K1 is 3 K2 is 3 c is 0.93
K1 is 3 K2 is 3 c is 0.94
K1 is 3 K2 is 3 c is 0.95
K1 is 3 K2 is 3 c is 0.96
K1 is 3 K2 is 3 c is 0.97
K1 is 3 K2 is 3 c is 0.98
K1 is 3 K2 is 4 c is 0.90
K1 is 3 K2 is 4 c is 0.91
K1 is 3 K2 is 4 c is 0.92
K1 is 3 K2 is 4 c is 0.93
K1 is 3 K2 is 4 c is 0.94
K1 is 3 K2 is 4 c is 0.95
K1 is 3 K2 is 4 c is 0.96
K1 is 3 K2 is 4 c is 0.97
K1 is 3 K2 is 4 c is 0.98
K1 is 4 K2 is 2 c is 0.90
K1 is 4 K2 is 2 c is 0.91
K1 is 4 K2 is 2 c is 0.92
K1 is 4 K2 is 2 c is 0.93
K1 is 4 K2 is 2 c is 0.94
K1 is 4 K2 is 2 c is 0.95
K1 is 4 K2 is 2 c is 0.96
K1 is 4 K2 is 2 c is 0.97
K1 is 4 K2 is 2 c is 0.98
K1 is 4 K2 is 3 c is 0.90
K1 is 4 K2 is 3 c is 0.91
K1 is 4 K2 is 3 c is 0.92
K1 is 4 K2 is 3 c is 0.93
K1 is 4 K2 is 3 c is 0.94
K1 is 4 K2 is 3 c is 0.95
K1 is 4 K2 is 3 c is 0.96
K1 is 4 K2 is 3 c is 0.97
K1 is 4 K2 is 3 c is 0.98
K1 is 4 K2 is 4 c is 0.90
K1 is 4 K2 is 4 c is 0.91
K1 is 4 K2 is 4 c is 0.92
K1 is 4 K2 is 4 c is 0.93
K1 is 4 K2 is 4 c is 0.94
K1 is 4 K2 is 4 c is 0.95
K1 is 4 K2 is 4 c is 0.96
K1 is 4 K2 is 4 c is 0.97
K1 is 4 K2 is 4 c is 0.98


                                                   Histogram of number of reference contigs

                       80 +-----------------------------------------------------------------------------------------+
                          |        +        +        +        +        *        +        +        +        +        |
                          |                                 'plot.kopt.*ata' using (bin($1,binwidth)):(1.0) ******* |
                       70 |-+                                          *                                          +-|
                          |                                            *                                            |
                          |                                            *                                            |
                       60 |-+                                          *                                          +-|
                          |                                            *                                            |
                          |                                            *                                            |
                       50 |-+                                          *                                          +-|
                          |                                            *                                            |
                       40 |-+                                          *                                          +-|
                          |                                            *                                            |
                          |                                            *                                            |
                       30 |-+                                          *                                          +-|
                          |                                            *                                            |
                          |                                            *                                            |
                       20 |-+                                          *                                          +-|
                          |                                            *                                            |
                          |                                            *                                            |
                       10 |-+                                          *                                          +-|
                          |                                            *                                            |
                          |        +        +        +        +        *        +        +        +        +        |
                        0 +-----------------------------------------------------------------------------------------+
                        1235.5    1236    1236.5    1237    1237.5    1238    1238.5    1239    1239.5    1240    1240.5
                                                          Number of reference contigs

Average contig number = 1234.74
The top three most common number of contigs
X	Contig number
41	1235
33	1234
3	1237
The top three most common number of contigs (with values rounded)
X	Contig number
81	1200
```

## Let's graph some more data


```{r}
library(ggplot2)

data.table <- read.table("kopt.data", header = FALSE, col.names= c("k1","k2","Similarity", "Contigs"))

data.table$K1K2 <- paste(data.table$k1, data.table$k2, sep=",")

df=data.frame(data.table)
df$K1K2 <- as.factor(df$K1K2)

p <- ggplot(df, aes(x=Similarity, y=Contigs, group=K1K2)) + scale_x_continuous(breaks=seq(0.8,0.98,0.01)) + geom_line(aes(colour = K1K2))
p
```

It seems like differentiation changes at about 97% with perhaps a secondary change at 92%

Let's try 96% (right after the inflection), but first we need to trim the read files

```{bash}
cat config
```

```{bash}
source activate Week5
dDocent config
```

No, let's run RefMapOpt

```{bash, eval=FALSE}
source activate Week5
RefMapOpt.sh
```

```
Usage is RefMapOpt minK1 maxK1 minK2 maxK2 cluster_similarity Assembly_Type Num_of_Processors optional_list_of_individuals
```




```{bash, eval=FALSE}
source activate Week5
RefMapOpt.sh 2 5 2 5 0.96 PE 48
```

```
Trimmed sequences found, proceeding with optimization.
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
[bam_sort_core] merging from 0 files and 48 in-memory blocks...
```

```{bash}
column -t -s $'\t' mapping.results
```


Here, we are maximizing our Mean Properly Paired Reads at K1=3 and K2=3 with a 1234 reference sequences


```{bash}
sort -k 10 -n -r  mapping.results | column -t -s $'\t'
```

```{bash}
cat config2
```


```{bash}
source activate Week5
dDocent config2
```



# The answer is 1234
