---
title: "Week11"
author: "JonPuritz"
date: "4/10/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# PCA and MDS for NGS

Exercise created by [Anders Albrechtsen](http://www.popgen.dk/groupWiki/index.php/Anders_Albrechtsen)

## Small intro with known genotypes

First lets input the genotype into R. First open R by typing 'R' in the command line:
 
```{r}
G <-matrix(c(1,0,2,0,2,0,2,1,1,1,0,1,0,2,1,2,1,1,1,1,1,0,1,0,2,0,1,1,0,2,1,2,0,1,0),5,by=T)
nInd <- nrow(G)

print(G)
```

Identify the rows and the columns. Does each row contain the genotypes of a site or an individual? And what about each column?

Let's try to do MDS. First let's calculate the distance. The simple distance measure as seen in the slides is called a Manhatten distance.
 
```{r}


D<-dist(G,upper=T,diag=T,method="manha")
D


```

-  How many dimensions are used to represent the distances?
 
Then reduce the dimension to 2 dimensions using MDS and plot the results:

```{r}
 ## continue in R	
 
 #perform MDS to 2 dimensions
 k2 <- cmdscale(D,k=2)
 print(k2)
```
 
```{r}
 #plot the results
 
 plot(k2,pch=16,cex=3,col=1:5+1,ylab="distance 2th dimension",xlab="distance 1.  dimension",main="Multiple dimension scaling (MDS)")
 points(k2,pch=as.character(1:5))
 
```

* Can you find a example of where the 2 dimensional representation does not capture the true pairwise distances?

First lets try to perform PCA directy on the normalized genotypes without calculating the covariance matrix

* Why do we normalize the genotypes?
 
```{r}
 #first normalize the data do that the mean and variance is the same for each SNP
  
 normalize <- function(x){
    nInd <- nrow(x)
    avg <- colMeans(x)
    M <- x - rep(colMeans(x),each=nInd)
    M <- M/sqrt(2*rep(avg/2*(1-avg/2),each=nInd))
    M
 }
 M <- normalize(G)

 svd <- svd(M)
 ## print the decomposition for M=SDV
 ## u is the eigenvectors
 ## d is eigen values  

 print(svd)
```

```{r}
##make a diagonal matrix with the eigenvalues 
SIGMA <- matrix(0,nInd,nInd)
diag(SIGMA) <- svd$d 

## using the matrixes from the decomposition we can undo the transformation of our normalized genotypes
M2 <- svd$u%*%SIGMA%*%t(svd$v)
print(M)
print(M2)

```

 - Did the reconstruction of the normalized genotypes work?
 - Would you be able to reconstruct the unnormalized (raw) genotypes?

Now try performing PCA based on the covariance matrix instead:

```{r}
 
 ## calculate the covariance matrix
 C <- M %*% t(M)
 print(C)
 
```

```{r}
 ## then perform the PCA by singular value decomposition
 e <- eigen(C)	 

 ## print first PC
 print(e$vectors[,1])
```

```{r} 
 ##plot 2 first PC. for the 5 indiviudals
 plot(e$vectors[,1:2],pch=16,cex=3,col=1:5+1,ylab="2. PC",xlab="1. PC",main="Principle component analysis (PCA)")
 points(e$vectors[,1:2],pch=as.character(1:5))
 ## don't close R
```

 - Did you get the same results using the covariance matrix as using the normalized genotypes directly?
 - What does negative values in the covariance matrix mean?
 - Compare the two plots (MDS vs. PCA)? 

Bonus information:

Unlike MDS, PCA will not remove information so you are actually able to reconstruct your covariance matrix from the principal components

```{r}
##continue in R
##make a diagonal matrix with the eigenvalues 
SIGMA <- matrix(0,nInd,nInd)
diag(SIGMA) <- e$value

## transform the PC back to the original data
## using matrix multiplication V SIGMA Vt
out <- e$vectors %*% SIGMA %*% t(e$vectors)
print(out)
```

```{r}
print(C)
```










 

